---
title: "Exploring and Analyzing Netflix Show User Reviews"
output: html_notebook
---

# Introduction
Netflix provides its users a plethora of shows to watch, all from different decades and different Genres. But how do these shows 
# Prerequisites
```{r Prerequsites, message=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(scales)
library(lubridate)
```
# DataSet

Import the required Netflix Data set, which can be found [Here!](https://raw.githubusercontent.com/reisanar/datasets/master/netflixShows.csv)
```{r}
#read the processed Data
netflixshows  <- read.csv('netflix_titles.csv')

# Delete the description and Show ID Columns
netflixshows <- netflixshows%>%
  select(-description, -show_id, - cast)

```

# Data Exploration and Analysis
## Exploring Single Variable Attributes

To get a better understanding of the data set as a whole, we've dissected certain factors that are crucial in the full understanding. In addition to separating variables, we ran several checks to ensure our data is not misleading, such as Dates being listed in the future or corrupted text.


### Content Type:

The visualization below graphically represents the distribution of the content released on Netflix's platform. They can either be labeled as a 'Movie' or a 'TV Show'.


```{r}
#Because countries are sometimes grouped together, separating them is required.
sep_country_movie <- netflixshows%>%
  separate_rows(country, sep = ",")%>%
  group_by(country)%>%
  #Due to the size of the dataset, we had to filter out countries that had under 100 Movie entries
  filter(n()> 100 & type == "Movie")%>%
  summarize(country)


```

### Country of Origin:
 This next visualization graphically demonstrates the distribution of content on Netflix per country. Content is separated by the Type of Content it is, either Movie or TV Show.
 
 
 **Netflix Movie Content by Country**
```{r}
#Because countries are sometimes grouped together, separating them is required.
  #Due to the size of the dataset, we had to filter out countries that had under 80 Movie entries.
netflixshows%>%
  separate_rows(country, sep = ",")%>%
  group_by(country)%>%
  filter(n()> 80 & type == "Movie" & country != "")%>%
  ggplot()+
    geom_bar(mapping = aes(
      y = country,
      color = country),
      na.rm = T)+
        labs(
          title = "Netflix Movie Content by Country",
          subtitle = "Includes Countries where count is more than 80",
          y = "Country Name",
          x = "Number of Movies"
        )
```
 **Netflix TV Show Content by Country**

```{r}
netflixshows%>%
  separate_rows(country, sep = ",")%>%
  group_by(country)%>%
  filter(n()> 80 & type == "TV Show" & country != "")%>%
  ggplot()+
    geom_bar(mapping = aes(
      y = country,
      color = country),
      na.rm = T)+
        labs(
          title = "Netflix TV Show Content by Country",
          subtitle = "Includes Countries where count is more than 80",
          y = "Country Name",
          x = "Number of TV Shows",
          
        )
    
```
### Year of Release:
Netflix has a wide range of films on their platform. Below is a graphical representation of the distributions of content by original release date, separated by both Movies and TV Shows.

**Netflix Movie content by Release Year**

```{r}
netflixshows%>%
  group_by(release_year)%>%
  filter(release_year != "" |  !is.na(release_year))%>%
  filter(type == "Movie")%>%
  ggplot()+
    geom_bar(mapping = aes(
      x = release_year))+
      labs(
          title = "Netflix Movie content by Release Year",
          x = "Year",
          y = "Count"
        )
```

**Netflix TV Show content by Release Year**
```{r}
netflixshows%>%
  group_by(release_year)%>%
  filter(release_year != "" |  !is.na(release_year))%>%
  filter(type == "TV Show")%>%
  ggplot()+
    geom_bar(mapping = aes(
      x = release_year))+
      labs(
          title = "Netflix Movie content by Release Year",
          x = "Year",
          y = "Count"
        )
```


### Age Rating:
Netflix rates all of their shows in a way that suggests appropriate ages see appropriate material. The graph below demonstrates the distribution between  Netflix's content and the associating Age rating.

```{r}
netflixshows%>%
  group_by(rating)%>%
  filter(rating != "" | !is.na(rating))%>%
  ggplot()+
  geom_bar(mapping = aes(
    y = rating,
    color = rating))+
    labs(
        title = "Netflix Content by Age Rating",
        x = "Count",
        y = "Age Rating"
      )
  
```






### Possible questions:
1. Amount of content as a function of time released
2. Is there a relationship between the rating of a show and the year of release?
3. Is there a possible relationship of mature ratings to user scores
4. Amount of content as a function of rating level
5. Does the director have a connection to the rating popularity?
6. Is there a popular connection with the shows and development of a specific country?
7. Is it possible for other countries to catch up from the number of shows compared to the United States in the future?
8. Does a specific director boost a country's popularity after a show's successful launch? Possibly creation inspiration for new and upcoming directors?
9. Will the release years be more varied?

# Conclusion

# Citations




