---
title: "Exploring and Analyzing Netflix Show User Reviews"
output: html_notebook
---

# Introduction
Netflix provides its users a plethora of shows to watch, all from different decades and different Genres. But how do these shows 
# Prerequisites
```{r Prerequsites}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(scales)
```
# DataSet

Import the required Netflix Dataset, which can be found [Here!](https://raw.githubusercontent.com/reisanar/datasets/master/netflixShows.csv)
```{r}
#read the processed Data
netflixshows  <- read.csv("https://raw.githubusercontent.com/reisanar/datasets/master/netflixShows.csv")
```

## Rating Classification
To simplify the range of user reviews, we've created a classification system.
```{r}
#Function to rate each show
netflixshows <- netflixshows%>%
  mutate(Rating_Classification = 
  ifelse(user.rating.score %in% 95:100,
        "5 Star",
  ifelse(user.rating.score %in% 90:94,
        "4-1/2 Star",
  ifelse(user.rating.score %in% 85:89,
         "4 Star",
  ifelse(user.rating.score %in% 80:84,
         "3-1/2 Star",
  ifelse(user.rating.score %in% 75:79,
         "3 Star",
  ifelse(user.rating.score %in% 70:74,
         "2-1/2 Star", 
  ifelse(user.rating.score %in% 65:69,
        "2 Star",
  ifelse(user.rating.score %in% 60:64,
        "1-1/2 Star",
  ifelse(user.rating.score %in% 55:59,
        "1 Star",
  ifelse(user.rating.score %in% 50:54,
        "1/2 Stars",
  ifelse(is.na(user.rating.score),
        "NA",
"0 Stars"))))))))))))%>%
  group_by(rating)
netflixshows
```

# Data Exploration and Analysis
### Possible questions:
1. Amount of content as a function of time released
2. Is there a relationship between the rating of a show and the year of release?
3. Is there a possible relationship of mature ratings to user scores
4. Amount of content as a function of rating level
5. Amount of content as a function of categorized ratings (5 stars, 4 stars, etc.)


# Conclusion

# Citations





```{r}
netflixshows %>%
  distinct()%>%
  arrange(-`release.year`)

ggplot(data = netflixshows) +
  geom_point(aes(x = `release.year`,
                 y = `user.rating.score`, na.rm = TRUE))
```
```{r}

```

